---
title: "Pandemic Terminator: An analysis of pandemic impacts and responses"
output:
  html_document: default
  pdf_document: default
---

```{r setup, ,warning=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r,include=FALSE}
library(tidyverse)
library(ggplot2)
library(rvest)
library(polite)
library(naniar)
library(gganimate)
library(gifski)
library(png)
library(plotly)
```

```{r,include=FALSE,warning=FALSE}
#Section 1. Scraping the data.

caseslink <- bow("https://en.wikipedia.org/wiki/COVID-19_pandemic_by_country_and_territory#Total_cases")
cases <- scrape(caseslink) %>% 
            html_nodes(xpath = '//*[@id="table65150380"]') %>%
            html_table()
head(cases)
```

```{r,warning=FALSE,include=FALSE}
##The number of cases and death for each country.
country_data <- cases[[1]] %>%
  select(-1,-6,-7,-8) 
#use the regular expression to remove the annotation behind the country name
country_data$Country = gsub('\\[.*]','',country_data$Country)
country_data[country_data == 'No data'] = NA

#convert the character into numeric
country_data$Deaths<-as.numeric(gsub(",","",country_data$Deaths))
country_data$Cases<-as.numeric(gsub(",","",country_data$Cases))
country_data$`Deaths/million`<-as.numeric(gsub(",","",country_data$`Deaths/million`))

write.csv(country_data, "Data/country_data.csv")
```

```{r,warning=FALSE,include=FALSE}
##Scrape the vaccine data
group_link <- bow("https://en.wikipedia.org/wiki/COVID-19_pandemic_by_country_and_territory#Total_cases")
group_data <- scrape(group_link) %>% 
            html_nodes(xpath = '//*[@id="covid19-container"]/table') %>%
            html_table()
head(group_data)
```
```{r,warning=FALSE,include=FALSE}
vaccine_data <- group_data[[3]] %>% 
  select(-1) %>% 
  rename(Country = 'Location',
         Vaccinated = 'Vaccinated[a]',
         Percentage = '%[b]')
vaccine_data$Country = gsub('\\[.*]','',vaccine_data$Country)

#convert the character into numeric
vaccine_data$Vaccinated<-as.numeric(gsub(",","",vaccine_data$Vaccinated))
vaccine_data$Percentage<-as.numeric(sub("%","", vaccine_data$Percentage))

write.csv(vaccine_data, "Data/vaccine_data.csv")
```

```{r,warning=FALSE,include=FALSE}
##Monthly data from 2020 to 2021
y2020_data <- group_data[[1]]
##should we use csv for analysis
write.csv(y2020_data, "Data/y2020_data.csv")

y2021_data <- group_data[[2]]
write.csv(y2021_data, "Data/y2021_data.csv")
```

```{r,warning=FALSE,include=FALSE}
##Scraping the GDP data
gdplink <- bow("https://en.wikipedia.org/wiki/List_of_countries_by_GDP_(PPP)_per_capita")
gdp_list <- scrape(gdplink) %>% 
            html_nodes(xpath = '//*[@id="mw-content-text"]/div[1]/table[1]') %>%
            html_table(header = FALSE) 
gdp <- gdp_list[[1]] %>% 
  select(-4,-5,-8,-9) %>% 
  rename(Country = X1,
         Subregion = X2,
         Region = X3,
         GDPperCap = X6,
         Year = X7) 
gdp <- gdp[-c(1,2),]
gdp$Country =gsub('\\*(.*)','',gdp$Country)

#convert the character into numeric
gdp$GDPperCap<-as.numeric(gsub(",","",gdp$GDPperCap))
write.csv(gdp, "Data/gdp.csv")
```


```{r,warning=FALSE,include=FALSE}
##Scraping the Population data
pop_link <-  bow("https://www.worldometers.info/world-population/population-by-country/")
pop <- scrape(pop_link) %>% 
            html_nodes(xpath = '//*[@id="example2"]') %>%
            html_table()
pop <- pop[[1]] %>% 
  select(-1) %>% 
  rename(Country = "Country (or dependency)")
write.csv(pop, "Data/pop.csv")
```


```{r}
#Section 2. Plotting and analysis.
country_data [-c(1),] %>% 
  top_n(20) %>% 
  ggplot(aes(x = reorder(Country,-Cases),  y= Cases, fill = Deaths ))+
  geom_col() +
  theme(axis.text.x=element_text(angle=45,size=10,hjust = 0.5,vjust=0.7))

```

```{r echo= FALSE}
##Merge the cases/deaths with population by "Country".
cases_pop <- country_data %>% 
  left_join(pop, by =  "Country") %>% 
  select(-c(11,12,13,14))

cases_pop$`Population (2020)`<-parse_number(cases_pop$`Population (2020)`)
cases_pop$`Density (P/Km²)`<-parse_number(cases_pop$`Density (P/Km²)`)
cases_pop$`Migrants (net)`<-parse_number(cases_pop$`Migrants (net)`)
cases_pop$`Land Area (Km²)`<- parse_number(cases_pop$`Land Area (Km²)`)
cases_pop$`Net Change`<-parse_number(cases_pop$`Net Change`)
cases_pop$`Yearly Change`<-parse_number(cases_pop$`Yearly Change`)
#changed to parse function helps with na values

#cases_pop <- na.omit(cases_pop)
```

Null Values:

```{r warning = FALSE}
miss_var_summary(cases_pop)
miss_case_summary(cases_pop)
```


```{r echo=FALSE}
##Dealing with missing values

#View the countries which are missing Data 
cases_pop%>% filter(is.na(`Deaths/million`))

country_data$
pop$Country

#changing the names of the countries that do not match
pop$Country[pop$Country == "Czech Republic (Czechia)"]<- "Czechia"
pop$Country[pop$Country == "State of Palestine"]<- "Palestine"
pop$Country[pop$Country == "Saint Kitts & Nevis" ]<- "Saint Kitts and Nevis"
pop$Country[pop$Country == "St. Vincent & Grenadines" ]<- "Saint Vincent and the Grenadines"
pop$Country[pop$Country == "Sao Tome & Principe" ]<- "Saint Kitts and Nevis"
pop$Country[pop$Country == "Congo" ]<- "Republic of the Congo"
pop$Country[pop$Country == "DR Congo" ]<- "Democratic Republic of the Congo"
pop$Country[pop$Country == "Micronesia" ]<- "Federated States of Micronesia"
pop$Country[pop$Country == "Ireland" ]<- "Republic of Ireland"
pop$Country[pop$Country == "Sao Tome & Principe" ]<- "Sao Tome and Principe"
pop$Country[pop$Country == "Côte d'Ivoire" ]<- "Ivory Coast"

#no data for vatican city but it only has a population of 850 odd people so really doesn't impact the data


#remove European union, world data and additional information column  (all countries that make up the union are individually included) and other columns are not relevant
country_data<- country_data[-c(1,196,34,38,194),]

#since there is no logical way to impute the date we remove the remaining variables with missing values 
cases_pop <- na.omit(cases_pop)

```

 Modeling Impacts of Covid 19:


```{r}
death_density <- ggplot(cases_pop, aes(x=log(`Density (P/Km²)`), y=log(`Deaths/million`),
                                       text = Country)) +
  geom_point() +
  ggtitle("Death rate Vs Density")

ggplotly(death_density)

```

```{r echo = FALSE}
##Merge the GDP data with cases and population
#remove the space at the end of country name
gdp$Country <- str_trim(gdp$Country)
#merge the GDP data with cases and population
cases_pop_gdp <- gdp %>% 
  left_join(cases_pop, by =  "Country")
cases_pop_gdp <- na.omit(cases_pop_gdp)
```
Regression, different variables to explain deaths.
```{r}
##Regression: How the number of cases, density, population and migrants affect the death rate.
death_density_reg <- lm(log(`Deaths/million`) ~  log(`Density (P/Km²)`)
                        +log(GDPperCap),
                        data = cases_pop_gdp)
summary(death_density_reg)
```
Q.1: How has GDP/Density impacted deaths across different regions.

In order to determine the extent of the detrimental effects of COVID-19, a metric must be chosen to represent/summarize the degree to which a country has been impacted by COVID-19. In the case of this analysis, the decided upon metric that most faithfully achieves this was determined to be Deaths per capita. Having established this the "Death rate Vs Density" scatter plot was constructed. Upon visual inspection of this graph, it can be interpreted that there is no clear relationship between deaths per capita and population density (measured in density per Km). In order to strengthen this contention, a linear regression was also plotted which included variables log(GDP per capita), log(density).  This regression supports the notion that there evidence of no relation as the p-value of the density regressor implies it is not statistically significant.


```{r}
#cases_pop_gdp$`Extimate.x`<-as.numeric(cases_pop_gdp$`Extimate.x`)
anim <- ggplot(cases_pop_gdp, aes(x= GDPperCap,
                                  y=`Deaths/million`,
                                  text = Country)) +
  geom_point(aes(colour = Region), size = 2)+
  labs(x='GDP per Capita')+
  ggtitle("Death rate Vs GDP/Cap")
ggplotly(anim)
```
Conversely to population density. GDP per capita does appear to share a positive relationship with deaths per million (from graph "Death rate Vs GDP/Cap") . That is the higher the GDP of a country the higher the death rate. This conclusion, continues if we look back the the regression, a p value of 1.68e-14 is given, suggesting little evidence against the null hypothesis that GDP and death rates are not correlated. 

from graph "Death rate Vs GDP/Cap", it would appear that Europe is heavily affected by Covid, where as the region of Africa and most Asian regions (with lower GDP's) also have very low Covid death rates. It can also be seen that The Americas are highly impacted by Covid as well.


Explaining Vaccination rates:
```{r echo = FALSE}
##Merge the Vaccine data
cases_pop_gdp_vax <- cases_pop_gdp %>% 
  left_join(vaccine_data, by =  "Country")
```

```{r}
##How the GDP per capita affects the vaccinate rate.
cases_pop_gdp_vax %>% 
  ggplot(aes(x=GDPperCap,
             y=Percentage,
             text = Country)) +
  geom_point(aes(colour = Region), size = 2) +
  labs(x='GDP per Capita',y = "Vaccinated Rate")+
  ggtitle("Vax Vs GDP")
ggplotly()
```
```{r}
cases_pop_gdp_vax %>% 
  ggplot(aes(x=log(`Density (P/Km²)`),
             y=Percentage,
             text = Country)) +
  geom_point(aes(colour = Region), size = 2) +
  labs(x='Pop Density',y = "Vaccinated Rate")+
  ggtitle("Pop Density Vs Vax Rate")
ggplotly()

```

```{r}
vaccine_reg <- lm(Percentage ~  log(Cases) + log(`Density (P/Km²)`) + log(`Population (2020)`)
                  + log(GDPperCap)+log(`Deaths/million`),
                  data = cases_pop_gdp_vax)
summary(vaccine_reg)
```
Q.2: Will the population density impact on the vaccination rates?

 In a similar style of analysis to the previous question in order to review the impacts of GDP per capita and population density upon vaccination rate, both scatter plot and regression analysis was conducted. Beginning with population density it can initially be inferred from the scatter plot, "pop density vs vax rate", that there is no strong correlation between the two variables, although it can be seen that African countries have a relatively low vaccination rate. Such a hypothesis is confirmed in the regression was we are able to see that population density is not statistically significant in predicting vaccination rate (p-value < 0.05)


Q.4:
Are the vaccination roll outs across the world, bias to richer countries?

From the regression above, The GDP per capita appears significant, which means the GDP has great impact on the vaccine rate. This can be seen from its p value, suggesting low evidence of the correlation of these two variables being 0. The GDP per capital increases 1% on average, the vaccine rate will increase 18.07%, holding other variables constant. Using the graph, "Vax rate Vs GDP" above, it can be seen clearly a strong positive relationship between the vaccination rates and GDP. This gives us an indication that vaccination rates are severely bias, and favored towards richer countries. This can be extrapolated to regions as well. From the graphic, the continent Africa can be seen, due to its lower GDP, has its countries distributed among very vaccination rates, where as the richer countries on average, Europe appear to be highly distributed with higher vaccination rates.

```{r warning = FALSE}
cases_pop_gdp_vax %>% 
  ggplot(aes(x=`Deaths/million`,
             y=Percentage,
             text = Country)) +
  geom_point(aes(colour = Region), size = 2) +
  labs(x='Deaths Rate',y = "Vaccinated Rate") + ggtitle("Vax rate Vs Death Rate")
ggplotly()
```
From the graph above, we can answer the question if countries impacted by covid have a better vaccination response. Qualitatively from this graphic above, the death rate does appear to have some positive correlation, Further more, the p value of 0.016 from the regression suggests there is little evidence of deaths and vaccination rates, not being correlated (coefficient of 0), reiterating the point that countries worse hit by covid appear to have smoother vaccination roll outs.

Time Series Analysis:

This section will look at how GDP, and vaccinations for the top and bottom countries from these two metrics change over time.

```{r echo = FALSE}
##Time series analysis, based on 2020 and 2021 data
#cleaning for time series data       
y2020_data <- as.data.frame(y2020_data)
y2020_data$Jan <-as.character(y2020_data$Jan)
y2020_data$Feb <-as.character(y2020_data$Feb)
```

```{r echo = FALSE}
#top 5 GDP/Capital country
#converting to long format
y2020_gdp_top5 <- y2020_data %>% 
  rename("Country" = '2020') %>% 
  filter(Country %in% c("Luxembourg","Singapore","Brunei","Qatar","United Arab Emirates")) %>% 
  pivot_longer(cols = c("Jan", "Feb","Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
             names_to = "month",
             values_to = "cases")
#cleaning long data
y2020_gdp_top5$month <- factor(y2020_gdp_top5$month, levels=c("Jan", "Feb","Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

y2020_gdp_top5$cases <- parse_number(y2020_gdp_top5$cases)

#merged the data to create new variable 
y2020_gdp_top5 <-y2020_gdp_top5  %>%
  inner_join(cases_pop, by = "Country")
y2020_gdp_top5 <- y2020_gdp_top5 %>%
  mutate(cases_per_capita = cases/`Population (2020)`) %>% 
  select(-4,-5,-6,-8,-9,-10,-11,-12) %>% 
  mutate(group = "top_5 GDP")
```

Creating the bottom and top 5 GDP for countries and Vaccination rates
```{r echo = FALSE}
#Bottom 5 GDP/Cap country
#converting to long format
y2020_gdp_bot5 <- y2020_data %>% 
  rename("Country" = '2020') %>% 
  filter(Country %in% c("Burundi","Somalia","Central African Republic","Niger","South Sudan")) %>% 
  pivot_longer(cols = c("Jan", "Feb","Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
             names_to = "month",
             values_to = "cases")
#cleaning long data
y2020_gdp_bot5$month <- factor(y2020_gdp_bot5$month, levels=c("Jan", "Feb","Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

y2020_gdp_bot5$cases <- parse_number(y2020_gdp_bot5$cases)

#merged the data to create new variable 
y2020_gdp_bot5 <-y2020_gdp_bot5  %>%
  inner_join(cases_pop, by = "Country")
y2020_gdp_bot5 <- y2020_gdp_bot5 %>%
  mutate(cases_per_capita = cases/`Population (2020)`) %>% 
  select(-4,-5,-6,-8,-9,-10,-11,-12) %>% 
  mutate(group="bot_5 GDP")
```

```{r}
#combine the GDP per Capital top_5 country and bottom_5 country 
comb_gdp <- bind_rows(y2020_gdp_top5,y2020_gdp_bot5)
```

```{r echo = FALSE}
#graph data
comb_gdp %>%
  group_by(group) %>% 
  ggplot(
      aes(x=month, y = cases_per_capita,group = 1,color = Country))+
  geom_line()+
  facet_grid(Country~group)+
  theme(axis.text.x = element_text(angle = 90))
```

Q.4a: How does cases effect the bottom and top 5 countries based on GDP:

We picked five countries with high GDP, and five countries with low GDP. From the corresponding time series chart, it can be seen that countries with high GDP are more affected by COVID-19. The number of cases in most countries shows an increasing trend, while the curve in countries with low GDP is relatively flat, indicating that countries with high GDP are at higher risk.


Time Series Cases, for bottom and top 5 vaccination rates
```{r echo = FALSE}
#top5 and bottom 5 Vaccination rate country
#converting to long format
y2020_vacc_top5 <- y2020_data %>% 
  rename("Country" = '2020') %>% 
  filter(Country %in% c("United Arab Emirates","Portugal","Cuba","Malta","Chile")) %>% 
  pivot_longer(cols = c("Jan", "Feb","Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
             names_to = "month",
             values_to = "cases")


y2020_vacc_top5$month <- factor(y2020_vacc_top5$month, levels=c("Jan", "Feb","Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

y2020_vacc_top5$cases <- parse_number(y2020_vacc_top5$cases)

#merged the data to create new variable 
y2020_vacc_top5 <-y2020_vacc_top5  %>%
  inner_join(cases_pop, by = "Country")
y2020_vacc_top5 <- y2020_vacc_top5 %>%
  mutate(cases_per_capita = cases/`Population (2020)`) %>% 
  select(-4,-5,-6,-8,-9,-10,-11,-12) %>% 
  mutate(group = "top_5 vax")
```

```{r echo = FALSE}
#converting to long format
y2020_vacc_bot5 <- y2020_data %>% 
  rename("Country" = '2020') %>% 
  filter(Country %in% c("Haiti","Madagascar","South Sudan","Chad","Tanzania")) %>% 
  pivot_longer(cols = c("Jan", "Feb","Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
            names_to = "month",
            values_to = "cases")

y2020_vacc_bot5$month <- factor(y2020_vacc_bot5$month, levels=c("Jan", "Feb","Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"))

y2020_vacc_bot5$cases <- parse_number(y2020_vacc_bot5$cases)

#merged the data to create new variable 
y2020_vacc_bot5 <-y2020_vacc_bot5  %>%
  inner_join(cases_pop, by = "Country")
y2020_vacc_bot5 <- y2020_vacc_bot5 %>%
  mutate(cases_per_capita = cases/`Population (2020)`) %>% 
  select(-4,-5,-6,-8,-9,-10,-11,-12) %>% 
  mutate(group = "bot_5 vax")
```
 
```{r echo = FALSE}
#combine the vaccination rate top_5 country and bottom_5 country 
comb_vacc <- bind_rows(y2020_vacc_top5,y2020_vacc_bot5)
```

```{r}
#graph data
comb_vacc %>%
  group_by(month) %>% 
  ggplot(
      aes(x=month, y = cases_per_capita,group = 1,color = Country))+
  geom_line()+
  facet_grid(Country~group)+
  theme(axis.text.x = element_text(angle = 90))
```


Q.4b: How does cases effect the bottom and top 5 countries based on vaccine rates:

Further, we identified five countries with high and five with low vaccination rates. As you can see from the chart, countries with high vaccination rates show a higher trend of increasing cases, which further suggests that increasing cases drive vaccination rates in these countries. The fact that countries continue to be impacted by covid despite high vaccine rates, could  come down to the delayed response vaccines will have, to improve countries' position in relation to covid. Potentially as time goes on, these trends could reverse.


Conclusion:

When analyzing the impacts of Covid across the world, fundamentally it appears richer countries have been impacted the worst in terms of cases and deaths. Wether this comes down to a lack of reporting from poorer countries, or has something to do with the viral characteristics of Covid itself, is a question still to be answered. From the vaccination rates, countries that are richer, also appear to have much more successful vaccination rates. This could be a combination of factors including the fact that not only have the resources to roll out vaccines, need it more as these countries have been disproportionally impacted by Covid-19. Finally, while this vaccination roll out is much more successful in rich countries, they still continue to be effected by Covid, potentially coming down to the delayed effect vaccinations will have on covid deaths.
